Survival Analysis of Questions Posted on the iFixit Answers Forum

### 2018-05-03 CSM_poster/main.tex
adjust spacing
spacing adjustments

@@

@@

% \vspace{1ex}
% 
% \textcolor{dblue!70}{\ding{228}} \textcolor{dblue!70}{\textbf{Assess Performance}} 
% 
% \vspace{0.5ex}

@@

\begin{table}[!htbp]
\captionsetup{skip=40pt}
\vspace{2ex}
\begin{tabular}{|r|r|r|r|r|r|r|r|}
  \hline
  & \textbf{HR} & \textbf{LR} & \textbf{p-value} & \textbf{$R^2$} & \textbf{\textit{Dxy}} & \textbf{C} \\
  \hline
  \textbf{Training} & 2.03 & 937.39  & \textless0.0001 & 0.14 & 0.27 & 0.63 \\
  \textbf{Test}     & 1.99 & 220.83  & \textless0.0001 & 0.14 & 0.26 & 0.63 \\
  \textbf{Full}     & 2.03 & 1165.03 & \textless0.0001 & 0.14 & 0.28 & 0.63 \\
  \hline
\end{tabular}
\caption{Performance metrics achieved in cross-validation and for the model fit to the full data (HR: Hazard Ratio, LR: Partial Likelihood Ratio, C: Concordance)}
\label{table:1}
\end{table}

@@

@@

@@

\textcolor{dblue!70}{\ding{228}} 25\% lower (95\% CI (19\%, 29\%)) for questions with titles containing at least one frequently-used word among unanswered question titles vs otherwise

@@

@@

\textcolor{dblue!70}{\ding{228}} Research was supported by the Bill and Linda Frost fund of California Polytechnic State University, San Luis Obispo. We also thank iFixit for providing access to the \textit{Answers} data.

>>>>

\vspace{2.5ex}

@@

\vspace{0.25ex}

@@

\vspace{0.25ex}

@@

\begin{table}[!htbp]
\captionsetup{skip=40pt}
\vspace{2.5ex}
\begin{tabular}{|r|r|r|r|r|r|r|r|}
  \hline
  & \textbf{HR} & \textbf{LR} & \textbf{p-value} & \textbf{$R^2$} & \textbf{\textit{Dxy}} & \textbf{C} \\
  \hline
  \textbf{Training} & 2.03 & 937.39  & \textless0.0001 & 0.14 & 0.27 & 0.63 \\
  \textbf{Test}     & 1.99 & 220.83  & \textless0.0001 & 0.14 & 0.26 & 0.63 \\
  \textbf{Full}     & 2.03 & 1165.03 & \textless0.0001 & 0.14 & 0.28 & 0.63 \\
  \hline
\end{tabular}
\caption{Performance metrics achieved in cross-validation and for the model fit to the full data (HR: Hazard Ratio, LR: Partial Likelihood Ratio, C: Concordance)}
\label{table:1}
\end{table}

\vspace{3ex}

@@

\vspace{0.35ex}

@@

\vspace{1.8ex}

@@

\textcolor{dblue!70}{\ding{228}} 25\% lower (95\% CI (19\%, 29\%)) for questions with titles containing at least one frequently-used word among unanswered questions vs otherwise

@@

\vspace{3ex}

@@

\small{\rmfamily{Research was supported by the Bill and Linda Frost fund of California Polytechnic State University, San Luis Obispo. We also thank iFixit for providing access to the \textit{Answers} data.}} \\
